### 2014-11-20 ms.Rmd
First version of manuscript support

```{r, results="hide", echo=FALSE, message=FALSE}
source("MS-fun.R")

knitr::opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="")
options(citation_format = "text", max.names=2)

bib <- read.bibtex("refs.bib")
baad <- readRDS("../output/baad.rds")
data <- baad$data
var.def <- read.csv("../config/variableDefinitions.csv",
                    stringsAsFactors=FALSE)

vars <- setdiff(var.def$variable[var.def$type == "numeric"], c("map","mat","lai","age"))
```

```{r,results="asis",echo=FALSE, message=FALSE}
details <- authorDetails(baad$contact)

writeLines(paste("**List of Authors:** ", paste0(details$authors, "^", details$address_code,"^",collapse = ", ") ))

writeLines("\n\n")

writeLines(paste0(details$address$code, ". ", details$address$address, collapse="\n"))

write.csv(data.frame(name=details$authors, email=details$emails, address=details$address$address[match(details$address_code, details$address$code)]), "../output/authors.csv", row.names=FALSE)
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}

# World plot colored by vegetation type
cols <- make.transparent(c(
    "blue","brown","forestgreen","darkorange","dodgerblue2",
    "navajowhite4","lightgoldenrod3","lavender"),0.67)
vegs <- c("BorF","Sav","TempF","TempRF","TropRF","TropSF","Wo")
vegs_labels <- c("Boreal forest","Savannah","Temperate forest",
                 "Temperate rainforest","Tropical rainforest",
                 "Tropical seasonal forest","Woodland","Glasshouse / Common garden")

drawWorldPlot(data[data$vegetation == vegs[1],], sizebyn=TRUE, pchcol=cols[1])
for(i in 2:length(vegs)){
  drawWorldPlot(data[data$vegetation == vegs[i],], sizebyn=TRUE, pchcol=cols[i], add=TRUE)
}
drawWorldPlot(data[data$growingCondition == "GH",], sizebyn=TRUE,
              pchcol=cols[8], add=TRUE)
par(xpd=NA)
legend(-160, -100, vegs_labels[1:4], fill=cols[1:4], bty='n')
legend(-40, -100, vegs_labels[5:8], fill=cols[5:8], bty='n')

```

@@

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)

## for debugging
# for(s in unique(data$studyName)){
#  cat(s)
#  studyDetails(data[data$studyName==s,])}

details2B  <-  daply(data, .(studyName), function(x) studyDetails(x))
writeLines(details2B,sep="\n\n")
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$variable,
    "\n\t- Type: ", x$type,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$description,
		"\n\t- Units: ", gsub(".","/", x$unitsMD, fixed=TRUE)
		))

writeLines(x[var.def$variable])
```

@@

```{r results='asis', echo=FALSE, warning=FALSE}
options(digits=9)
kable(summaryTable(data, var.def), "markdown", align="l", padding=10)
```

@@

In addition, we thank the following people for contributions to the following studies:
```{r,results="asis",echo=FALSE, message=FALSE}
getAcknowledgments <- function(studyName) {
  metadata  <-  readStudyFile(studyName, "studyMetadata.csv")
  i <- match("Acknowledgements",metadata$Topic)
  out <- ""
  if(!is.na(i))
    out <- sprintf(" **%s:** %s;", studyName, metadata$Description[i])
  out
}
writeLines(paste(sapply(unique(data$studyName), getAcknowledgments), collapse= ""))
```
.

>>>>

```{r, results="hide", echo=FALSE, message=FALSE}
knitr::opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="")
options(citation_format = "text", max.names=2)

bib <- read.bibtex("refs.bib")
data <- baad$data
var_def <- baad$dictionary
vars <- setdiff(var_def$variable[var_def$type == "numeric"], 
                c("map", "mat", "lai", "age"))
```

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:** ", 
                 paste0(author_info$authors$name, 
                        "^", author_info$authors$address_code, "^", 
                        collapse = ", ")))
writeLines("\n\n")
writeLines(paste0(author_info$address_table$code, ". ", 
                  author_info$address_table$address))
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
# World plot colored by vegetation type
cols <- make_transparent(c(
    "blue","brown","forestgreen","darkorange","dodgerblue2",
    "navajowhite4","lightgoldenrod3","lavender"),0.67)
vegs <- c("BorF","Sav","TempF","TempRF","TropRF","TropSF","Wo")
vegs_labels <- c("Boreal forest","Savannah","Temperate forest",
                 "Temperate rainforest","Tropical rainforest",
                 "Tropical seasonal forest","Woodland","Glasshouse / Common garden")

drawWorldPlot(data[data$vegetation == vegs[1],], sizebyn=TRUE, pchcol=cols[1])
for(i in 2:length(vegs)){
  drawWorldPlot(data[data$vegetation == vegs[i],], sizebyn=TRUE, pchcol=cols[i], add=TRUE)
}
drawWorldPlot(data[data$growingCondition == "GH",], sizebyn=TRUE,
              pchcol=cols[8], add=TRUE)
par(xpd=NA)
legend(-160, -100, vegs_labels[1:4], fill=cols[1:4], bty='n')
legend(-40, -100, vegs_labels[5:8], fill=cols[5:8], bty='n')
```

@@

```{r,results="asis",echo=FALSE, message=FALSE}
details2B <- sapply(split(data, data$studyName), study_details, baad)
writeLines(details2B, sep="\n\n")
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
writeLines(variable_details(var_def))
```

@@

```{r results='asis', echo=FALSE, warning=FALSE}
options(digits=9)
kable(summary_table(data, var_def), "markdown", align="l", padding=10)
```

@@

In addition, we thank the following people for contributions to the following studies:
```{r,results="asis",echo=FALSE, message=FALSE}
ack <- sapply(unique(data$studyName), get_acknowledgements)
writeLines(paste(ack, collapse=""))
```
.
